Towards Verifying the Bitcoin-S Library

### 2019-07-06 paper/paper.tex
remover some double spaces
update todos

\paragraph{The Bitcoin-S Library.} The bitcoin-s library is an
implementation of parts of the Bitcoin protocol in Scala
\cite{BitcoinS:website,BitcoinS:github}. In particular, it allows to
serialize, deserialize, sign and validate Bitcoin transactions. The library
uses immutable data structures and algebraic data types but is not
written with formal verification in mind. According to the website,
the library is used in production, handling significant amounts of
cryptocurrency each day \cite{BitcoinS:website}.

@@

On the other hand, bitcoin-s uses features that might not be supported
even by future Stainless versions, such as (concrete, non-case)
classes \todo{NOT TRUE, no classes found} or calls to Java code. Here
the bitcoin-s code can hopefully be adapted to accommodate formal
verification.

@@

\todo{reference to verified code} \todo{say which version of stainless
  we used, which version of bitcoin-s:
  91633375a37a170ba260ff4b443582aca4aa0c77 }

>>>>

\paragraph{The Bitcoin-S Library.} The bitcoin-s library is an
implementation of parts of the Bitcoin protocol in Scala
\cite{BitcoinS:website,BitcoinS:github}. In particular, it allows to
serialize, deserialize, sign and validate Bitcoin transactions. The
library uses immutable data structures and algebraic data types but is
not specifically written with formal verification in mind. According
to the website, the library is used in production, handling
significant amounts of cryptocurrency each day
\cite{BitcoinS:website}.

@@

On the other hand, bitcoin-s uses features that might not be supported
even by future Stainless versions, such as calls to Java code. Here
the bitcoin-s code can hopefully be adapted to accommodate formal
verification.

@@

\todo{reference to verified code}

\todo{say which version of stainless
  we used, which version of bitcoin-s:
  91633375a37a170ba260ff4b443582aca4aa0c77 }
